---
title: "Testing broom.mixed for spaMM"
author: "Alexandre Courtiol"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    toc: yes
    toc_depth: 4
vignette: >
  %\VignetteIndexEntry{Testing broom.mixed for spaMM}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE, message=FALSE}
library(knitr)
options(tibble.width = Inf)
```

## Introduction

This vignette aims at testing the methods `tidy()`, `glance()` and `augment()` for the class of model `HLfit` produced by the R package `{spaMM}`.

We use this vignette during the development of these methods to make sure that the correct outputs are obtained under various conditions.

We will also compare the outputs with those produced by equivalent methods implemented in other packages fitting mixed and non-mixed packages.

For this, we start by loading the packages required for this vignette
```{r loading libraries, message=FALSE}
library("broom")
library("broom.mixed")
library("spaMM")
library("lme4")
library("glmmTMB")
```

## Homoscedastic LM

### Fitting models
```{r lm1}
lm1_lm <- lm(Sepal.Length ~ Species, data  = iris)
lm1_spaMM_fitme <- fitme(Sepal.Length ~ Species, data  = iris)
```

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
```{r glance lm1}
glance(lm1_lm)
glance(lm1_spaMM_fitme)
glance(lm1_spaMM_fitme, npar.details = TRUE)
```

#### FIXME?
Some statistics produced by `glance.lm()` are missing from `glance.HLfit()`:
- `r-squared` \& `adj.r.squared` statistics $\rightarrow$ unlikely to work in general unless new function appear in spaMM, so perhaps it makes sense to skip it
- `p.value` \& `df` $\rightarrow$ this corresponds to a test with a null model $\rightarrow$  unlikely to work in general so perhaps it makes sense to skip it
- `BIC` $\rightarrow$  I don't know if there is a general version of it for GLMM...


## Heteroscedastic LM

### Fitting models
```{r lm2, message=FALSE}
lm2_glmmTMB <- glmmTMB(Sepal.Length ~ Species, dispformula = ~ Species, data  = iris)
lm2_spaMM_fitme <- fitme(Sepal.Length ~ Species, resid.model = ~ Species, data  = iris)
```

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
```{r glance lm2}
glance(lm2_glmmTMB)
glance(lm2_spaMM_fitme)
```

## Idiosyncratic LM

### Fitting models
```{r lm3_4, message=FALSE}
lm3_spaMM_fitme <- fitme(Sepal.Length ~ -1, data  = iris) ## no estimate
lm4_spaMM_fitme <- fitme(Sepal.Length ~ Petal.Length, data  = iris,
                         etaFix = list(beta = c("Petal.Length" = 0.5)))  ## fixed estimate
```

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
```{r glance lm3_4}
glance(lm3_spaMM_fitme)
glance(lm4_spaMM_fitme)
```

#### FIXME?
These cases do not seem to be handled properly $\rightarrow$ the question is whether we should deal with them and detect such cases and produce a warning

## Poisson GLM

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
TO COME


## Binomial GLM

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
TO COME

## Negative Binomial GLM

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
TO COME

## COM-Poisson GLM

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
TO COME

## Zero truncated GLM

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
TO COME

## LMM with 1 simple random effect

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
TO COME

## LMM with 2 simple random effect

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
TO COME

## LMM with random slopes

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
TO COME

## LMM with autocorrelation

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
TO COME

## LMM with correlation matrix

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
TO COME

## DHLM

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
TO COME


## GLMM

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
TO COME

## DHGLM

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
TO COME


## Multivariate fits

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
TO COME
