---
title: "Testing broom.mixed for spaMM"
author: "Alexandre Courtiol & François Rousset"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    toc: yes
    toc_depth: 4
vignette: >
  %\VignetteIndexEntry{Testing broom.mixed for spaMM}
  \usepackage[utf8]{inputenc}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, message=FALSE}
library(knitr)
options(tibble.width = Inf)
```

## Introduction

This vignette aims at testing the methods `tidy()`, `glance()` and `augment()` for the class of model `HLfit` produced by the R package `{spaMM}`.

We use this vignette during the development of these methods to make sure that the correct outputs are obtained under various conditions.

We will also compare the outputs with those produced by equivalent methods implemented in other packages fitting mixed and non-mixed packages.

For this, we start by loading the packages required for this vignette
```{r loading libraries, message=FALSE}
library("broom")
library("broom.mixed")
library("spaMM")
library("lme4")
library("glmmTMB")
library("MASS")
```

## Homoscedastic LM

### Fitting models
```{r lm1}
lm1_lm <- lm(Sepal.Length ~ Species, data  = iris)
lm1_spaMM_fitme <- fitme(Sepal.Length ~ Species, data  = iris)
```

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
```{r glance lm1}
glance(lm1_lm)
glance(lm1_spaMM_fitme)
glance(lm1_spaMM_fitme, npar.details = TRUE)
```

#### FIXME?
Some statistics produced by `glance.lm()` are missing from `glance.HLfit()`:

- `r-squared` \& `adj.r.squared` statistics $\rightarrow$ unlikely to work in general unless new function appear in spaMM, so perhaps it makes sense to skip it
- `p.value` \& `df` $\rightarrow$ this corresponds to a test with a null model $\rightarrow$  unlikely to work in general so perhaps it makes sense to skip it
- `BIC` $\rightarrow$  I don't know if there is a general version of it for GLMM...


## Heteroscedastic LM

### Fitting models
```{r lm2, message=FALSE, warning=FALSE}
lm2_glmmTMB <- glmmTMB(Sepal.Length ~ Species, dispformula = ~ Species, data  = iris)
lm2_spaMM_fitme <- fitme(Sepal.Length ~ Species, resid.model = ~ Species, data  = iris)
```

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
```{r glance lm2}
glance(lm2_glmmTMB)
glance(lm2_spaMM_fitme)
```

#### FIXME?
- here we could drop the column `sigma` but perhaps it is best to keep it for enforcing a consistent output


## Idiosyncratic LM

### Fitting models
```{r lm3_4, message=FALSE}
lm3_spaMM_fitme <- fitme(Sepal.Length ~ -1, data  = iris) ## no estimate
lm4_spaMM_fitme <- fitme(Sepal.Length ~ Petal.Length, data  = iris,
                         etaFix = list(beta = c("Petal.Length" = 0.5)))  ## fixed estimate
```

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
```{r glance lm3_4}
glance(lm3_spaMM_fitme)
glance(lm4_spaMM_fitme)
```

#### FIXME?
These cases do not seem to be handled properly $\rightarrow$ the question is whether we should deal with them and detect such cases and produce a warning

## Poisson GLM

### Fitting models
```{r glm_pos, warning=FALSE}
glm_pois_log_glm <- glm(total.fruits ~ amd, family = poisson(link = "log"), data = Arabidopsis)
glm_pois_log_glmmTMB <- glmmTMB(total.fruits ~ amd, family = poisson(link = "log"), data = Arabidopsis)
glm_pois_log_fitme <- fitme(total.fruits ~ amd, family = poisson(link = "log"), data = Arabidopsis)
```

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
```{r glance glm_pos}
glance(glm_pois_log_glm)
glance(glm_pois_log_glmmTMB)
glance(glm_pois_log_fitme)
```

#### Fixme?

- `glance.glm()` compares the model to a null model, albeit with no test $\rightarrow$ shall we do that?
- again, we could drop the column `sigma` but perhaps it is best to keep it for enforcing a consistent output, or as `glance.glmmTMB()` we could indicate overdispersion as `sigma` (nb: they did not document that)...?

## Binomial GLM

### Fitting models
```{r glm_binom, warning=FALSE}
glm_binom_logit_glm <- glm(cbind(incidence, size - incidence) ~ period, family = binomial(link = "logit"), data = cbpp)
glm_binom_logit_glmmTMB <- glmmTMB(cbind(incidence, size - incidence) ~ period, family = binomial(link = "logit"), data = cbpp)
glm_binom_logit_fitme <- fitme(cbind(incidence, size - incidence) ~ period, family = binomial(link = "logit"), data = cbpp)
```

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
```{r glance glm_binom}
glance(glm_binom_logit_glm)
glance(glm_binom_logit_glmmTMB)
glance(glm_binom_logit_fitme)
```


## Negative Binomial GLM

### Fitting models
```{r glm_negbin}
glm_negbin_log_glm.nb <- glm.nb(total.fruits ~ amd, data = Arabidopsis)
glm_negbin_log_fitme <- fitme(total.fruits ~ amd, family = negbin(link = "log"), data = Arabidopsis)
```

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
```{r glance glm_negbin}
glance(glm_negbin_log_glm.nb)
glance(glm_negbin_log_fitme)
glance(glm_negbin_log_fitme, npar.details = TRUE)
```

#### FIXME?

- I counted one extra parameter for this family (for the estimation of the `shape` parameter), but `glance.negbin()` does not (it relies internally on `glm_negbin_log_glm.nb$df.residual`, which does not factor `shape` in the computation). Who is correct?


## COM-Poisson GLM

### Fitting models
TO COME

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
TO COME

## Zero truncated GLM

### Fitting models
TO COME

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
TO COME

## LMM with 1 simple random effect

### Fitting models
TO COME

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
TO COME

## LMM with 2 simple random effects

### Fitting models
TO COME

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
TO COME

## LMM with random slopes

### Fitting models
TO COME

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
TO COME

## LMM with autocorrelation

### Fitting models
TO COME

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
TO COME

## LMM with correlation matrix

### Fitting models
TO COME

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
TO COME

## DHLM

### Fitting models
TO COME

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
TO COME


## GLMM

### Fitting models
TO COME

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
TO COME

## DHGLM

### Fitting models
TO COME

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
TO COME


## Multivariate fits

### Fitting models
TO COME

### Outputs from `tidy()`
TO COME

### Outputs from `augment()`
TO COME

### Outputs from `glance()`
TO COME
